\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-22 notes/notes.tex
typo

where we have identitied site \(i\) in the auxiliary model as the impurity.

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn} 

@@

\section{Analytic consistency check - On the Bethe lattice}
Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{green_eq_final_siam}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma \to 0
\end{aligned}\end{equation}
There we used the fact since at half-filling on an $SU(2)$ symmetric model, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\Phi_0} = \sum_n d^p_n \ket{\Phi_n}$ and \(c^\dagger_{i+1,\sigma}\ket{\Phi_0}=z^p_n\ket{\Phi_n}\) are constrained such that $\sum_n |d^p_n|^2 = \sum_n |z^p_n|^2 = \frac{1}{2}$, so that the only term that scales with $w$ is $w$ itself. This result then implies that $G^{H-H}$ matrix has no $k$ dependence.

>>>>

where we have identified site \(i\) in the auxiliary model as the impurity.

@@

	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn} 

@@

\section{Analytic consistency check - On the Bethe lattice}
One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{green_eq_final_siam}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma \to 0
\end{aligned}\end{equation}
There we used the fact since at half-filling on an $SU(2)$ symmetric model, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\Phi_0} = \sum_n d^p_n \ket{\Phi_n}$ and \(c^\dagger_{i+1,\sigma}\ket{\Phi_0}=z^p_n\ket{\Phi_n}\) are constrained such that $\sum_n |d^p_n|^2 = \sum_n |z^p_n|^2 = \frac{1}{2}$, so that the only term that scales with $w$ is $w$ itself. This result then implies that $G^{H-H}$ matrix has no $k$ dependence.
